---
title: "Survey Markdown"
author: "Group 16"
date: "2023-06-11"
output: pdf_document
---

```{r}
library(ggplot2)
library(dplyr)
library("tidyverse")
#install.packages("gridExtra")
library(gridExtra)

```

# The Impact of Online Learning on Technical Education During the Pandemic



```{r}
data <- read.csv("group_16.csv", header= TRUE, sep=";")
# preprocessing

# Split the string into parts
split_parts <- strsplit(data$Antwort.1, "; ")
split_parts2 <- strsplit(data$Antwort.2, "; ")
split_parts3 <- strsplit(data$Antwort.3, "; ")

# Create new columns based on split parts
new_columns <- t(sapply(split_parts, function(x) {
  parts <- strsplit(x, ": ")
  setNames(as.numeric(sapply(parts, function(y) y[2])), sapply(parts, function(y) paste0("Antwort1", y[1])))
}))

new_columns2 <- t(sapply(split_parts2, function(x) {
  parts <- strsplit(x, ": ")
  setNames(as.numeric(sapply(parts, function(y) y[2])), sapply(parts, function(y) paste0("Antwort2", y[1])))
}))

new_columns3 <- t(sapply(split_parts3, function(x) {
  parts <- strsplit(x, ": ")
  setNames(sapply(parts, function(y) y[2]), sapply(parts, function(y) paste0("Antwort3", y[1])))
}))

# Combine the new columns with the original data frame
data_p <- cbind(data[c(1,2,3)], new_columns, new_columns2, new_columns3)

# Rename the columns
colnames(data_p) <- c("gender", "age", "academic.program",
                    "test.prep.dur", "test.prep.bef","test.prep.af","ects.fail.dur","semesters.dur",
                    "ects.fail.bef","semesters.bef","ects.fail.af","semesters.af",
                    "source.dur","source.bef","source.af")


# Replace values based on condition
data_p$academic.program <- ifelse(grepl("Data Science", data_p$academic.program), "Data Science / MSc / TU WIen", data_p$academic.program)

data_p$gender = as.factor(data_p$gender)
data_p$academic.program = as.factor(data_p$academic.program)
data_p$source.dur = as.factor(data_p$source.dur)
data_p$source.bef = as.factor(data_p$source.bef)
data_p$source.af = as.factor(data_p$source.af)

#remove NaN
data_p = na.omit(data_p)

```

### What was the average time required for test preparation during and before/after the pandemic (in hours)

1. `pivot_longer`: This function is used to convert the data frame `data_p` from wide format to long format. It takes three columns (`test.prep.bef`, `test.prep.dur`, `test.prep.af`) and pivots them into two columns: `Period` and `Hours`. The `Period` column contains the names of the original three columns, and the `Hours` column contains the corresponding values.

2. `group_by` and `summarize`: These functions are used together to calculate statistics for each time period (`Before`, `During`, `After`). The `group_by` function groups the data by the `Period` column, and the `summarize` function calculates three statistics: `Mean` (average), `Median`, and `SD` (standard deviation) of the `Hours` column within each time period.

3. `print`: This function is used to print the formatted statistics to the console.

4. `ggplot`: This function is used to create a boxplot visualization. It takes the `data_p` data frame (excluding the 21st row) as input.

5. `geom_boxplot`: These functions are used to add boxplots to the plot for each time period. They specify the aesthetics (`aes`) mapping the x-axis to the time period (`"Before"`, `"During"`, `"After"`) and the y-axis to the corresponding columns (`test.prep.bef`, `test.prep.dur`, `test.prep.af`). The `fill` parameter sets the colors for the boxplots, and the `color` parameter sets the color for the outline.

6. `labs`: This function is used to set the labels for the x-axis, y-axis, and title of the plot.

7. `scale_x_discrete`: This function is used to set custom labels for the x-axis, mapping the original time period names to more descriptive labels.


```{r}
#print out statistics
# Convert the data frame to long format
data_long <- data_p %>%
  pivot_longer(cols = c(test.prep.bef,test.prep.dur,test.prep.af), names_to = "Period", values_to = "Hours")

# Calculate statistics for each time period
statistics <- data_long %>%
  group_by(Period) %>%
  summarize(
    Mean = mean(Hours),
    Median = median(Hours),
    SD = sd(Hours)
  )

# Print the formatted statistics
print(statistics)



# Create a boxplot for each column
# we exclude row 21 because of unrealistic values
ggplot(data_p[-20,]) +
  geom_boxplot(aes(x = "Before", y = test.prep.bef), fill = "lightblue", color = "black") +
  geom_boxplot(aes(x = "During", y = test.prep.dur), fill = "lightgreen", color = "black") +
  geom_boxplot(aes(x = "After", y = test.prep.af), fill = "lightyellow", color = "black") +
  labs(x = "Time Period", y = "Hours", title = "Average Test Preparation Hours Comparison") +
  scale_x_discrete(labels = c("Before" = "Before COVID-19", "During" = "During COVID-19", "After" = "After COVID-19"))
```

Based on the graph, we observe that the average test preparation before COVID was the highest, with an average of 29.4 hours per test. The median for this period was also the highest at 20 hours, indicating a wider range of preparation times. Notably, 25% of the students required more than 30 hours of learning time per test during this period.

During COVID, there was a significant decrease in preparation time, which suggests the possibility of more efficient study practices (assuming successful exams during that period). This observation is interesting considering that the university was closed and access to learning materials was limited. 

After the pandemic, we can see a median learning time of 15 hours. This trend indicates that the shift to online lectures and 24/7 availability of uploaded materials contributed to increased studying efficiency during the COVID pandemic.


### How many ECTS/semester did you fail on the first try during/before/after the pandemic period? (Example Answer: During the pandemic I did 4 Semesters and failed 6 ECTS)

1. `mutate`: This function is used multiple times to create new columns in the `data_p` data frame. The `mutate` function calculates and assigns values to the new columns `performance_dur`, `performance_bef`, and `performance_af`. These columns are derived by dividing the corresponding columns (`ects.fail.dur`, `ects.fail.bef`, `ects.fail.af`) by the corresponding columns (`semesters.dur`, `semesters.bef`, `semesters.af`).

2. `summarise`: This function is used to calculate summary statistics for the `data_p` data frame. It computes the mean of the `performance_dur`, `performance_bef`, and `performance_af` columns while excluding any non-finite values (`is.finite`) and removing any missing values (`na.rm = TRUE`). The resulting statistics are assigned to the `stats` data frame.

3. `data.frame`: This function is used to create a new data frame called `performance`. It combines the performance metrics for all periods (during, before, after) into a single data frame with two columns: `period` and `performance`. The `period` column is created using the `rep` function to repeat the time period labels, and the `performance` column combines the corresponding performance values from `data_p`. The argument `stringsAsFactors = FALSE` ensures that character vectors are not automatically converted to factors.

4. `geom_histogram`: These functions are used to create histograms for each period using the `ggplot` package. They specify the aesthetics (`aes`) mapping the x-axis to the respective performance columns (`performance_bef`, `performance_dur`, `performance_af`). The `binwidth` parameter determines the width of the bins in the histogram. The `fill` parameter sets the fill color of the histogram bars, and the `alpha` parameter controls the transparency. The `color` parameter sets the color of the outline of the bars.

5. `labs`: This function is used to set the x-axis and y-axis labels for the histograms.

6. `ggtitle`: This function is used to set the title of each histogram.

7. `theme_minimal`: This function is used to set a minimalistic theme for the histograms.

8. `geom_vline`: These functions are used to add vertical dashed lines to each histogram, indicating the mean value of the respective performance column. The `xintercept` aesthetic specifies the x-coordinate of the vertical line.

9. `grid.arrange`: This function is used to arrange the histograms in subplots. It takes the individual histograms (`hist_bef`, `hist_dur`, `hist_af`) as arguments and arranges them in a single row (`nrow = 1`). The `bottom` parameter is used to add a bottom label to the subplot.

```{r}

#head(data_p[c(7:12)])
data_p <- data_p %>% 
  mutate(performance_dur = ects.fail.dur / semesters.dur) %>%
  mutate(performance_bef = ects.fail.bef / semesters.bef) %>%
  mutate(performance_af = ects.fail.af / semesters.af)

#print out statistics
stats <- data_p %>%
  summarise(
    Performance_Dur = mean(performance_dur[is.finite(performance_dur)], na.rm = TRUE),
    Performance_Bef = mean(performance_bef[is.finite(performance_bef)], na.rm = TRUE),
    Performance_Af = mean(performance_af[is.finite(performance_af)], na.rm = TRUE)
  )

print(stats)


# Combine the performance metrics for all periods into a single data frame
performance <- data.frame(
  period = rep(c("During", "Before", "After"), each = nrow(data_p)),
  performance = c(data_p$performance_dur, data_p$performance_bef, data_p$performance_af),
  stringsAsFactors = FALSE
)

# Create separate histograms for each period
hist_bef <- ggplot(data_p, aes(x = performance_bef)) +
  geom_histogram(binwidth = 2, fill = "red", alpha = 0.7, color="black") +
  labs(x = "", y = "Count") +
  ggtitle("Before COVID-19") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) +
  geom_vline(aes(xintercept = mean(performance_bef)), color = "black", linetype = "dashed")

hist_dur <- ggplot(data_p, aes(x = performance_dur)) +
  geom_histogram(binwidth = 2, fill = "green", alpha = 0.7, color="black") +
  labs(x = "", y = "Count") +
  ggtitle("During COVID-19") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) +
  geom_vline(aes(xintercept = mean(performance_dur)), color = "black", linetype = "dashed")

hist_af <- ggplot(data_p, aes(x = performance_af)) +
  geom_histogram(binwidth = 2, fill = "blue", alpha = 0.7, color="black") +
  labs(x = "", y = "Count") +
  ggtitle("After COVID-19") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) +
  geom_vline(aes(xintercept = mean(performance_af)), color = "black", linetype = "dashed")


# Arrange the histograms in subplots
subplot <- grid.arrange(hist_bef, hist_dur, hist_af, nrow = 1,
                        bottom="failed ECTS / attended Semester Ratio")

# Display the subplots
subplot

```
In this plot, we analyze the performance of students in three periods. We examine the ratio between failed semesters and attended semesters for each student in each period. If a student did not study before COVID, their score would be NaN and therefore not included in the graph. Thus, we only observe data from students who studied during a particular period. A score of zero indicates that no ECTS (European Credit Transfer and Accumulation System) were failed during the attended semesters.

The average performance ratio before COVID was 1.13, during COVID it was 1.0, and after COVID it was 1.11. The performance during COVID was the best. However, we notice an improvement in performance when comparing the data from before and after COVID. It is important to note that the chart depicting the data from before COVID is not as well-populated as the others. This is because only a few students started their studies during COVID. Nonetheless, we observe that over five students achieved a performance ratio of about 2, and we also see a few students with a similar performance ratio after COVID.


```{r}
# Calculate the frequency of each label
label_counts <- table(data_p$source.bef)
label_counts2 <- table(data_p$source.dur)
label_counts3 <- table(data_p$source.af)

# Convert counts to proportions
label_proportions <- prop.table(label_counts)
label_proportions2 <- prop.table(label_counts2)
label_proportions3 <- prop.table(label_counts3)

# Create a data frame for plotting
plot_data <- data.frame(labels = names(label_proportions),
                        proportions = label_proportions)
plot_data2 <- data.frame(labels = names(label_proportions2),
                        proportions = label_proportions2)
plot_data3 <- data.frame(labels = names(label_proportions3),
                        proportions = label_proportions3)

# Create a pie plot using ggplot2
pie_plot <- ggplot(plot_data, aes(x = "", y = proportions.Freq, fill = labels)) +
  geom_bar(stat = "identity", width = 1, color="white") +
  coord_polar("y", start = 0) +
  #scale_fill_discrete(name = "Labels") +
  labs(title = "Before Corona") +
  geom_text(aes(label = paste0(round(proportions.Freq * 100, 2), "%")), position = position_stack(vjust = 0.5))+
  theme_void()+
  theme(legend.position = "none")

pie_plot2 <- ggplot(plot_data2, aes(x = "", y = proportions.Freq, fill = labels)) +
  geom_bar(stat = "identity", width = 1, color="white") +
  coord_polar("y", start = 0) +
  #scale_fill_discrete(name = "Labels") +
  geom_text(aes(label = paste0(round(proportions.Freq * 100, 2), "%")), position = position_stack(vjust = 0.5))+
  labs(title = "During Corona") +
  theme_void()+
  theme(legend.position = "none")

pie_plot3 <- ggplot(plot_data3, aes(x = "", y = proportions.Freq, fill = labels)) +
  geom_bar(stat = "identity", width = 1, color="white") +
  coord_polar("y", start = 0) +
  scale_fill_discrete(name = "Labels") +
  geom_text(aes(label = paste0(round(proportions.Freq * 100, 2), "%")), position = position_stack(vjust = 0.5))+
  labs(title = "After Corona") +
  theme_void()
  #theme(legend.position = "none")

# Arrange the histograms in subplots
subplot <- grid.arrange(pie_plot,pie_plot2,pie_plot3, nrow = 1,
                        bottom="Proportion of Learning Source")

# Display the subplots
subplot

```
In this pie chart, we observe a noticeable rise in the demand for external lecture data, such as YouTube videos or online papers. Before COVID, only 18.92% of students primarily consumed external learning material not provided by the university. However, during COVID, this percentage increased significantly to over 37.84%. Even after COVID, a substantial portion, 24.32%, continued to rely on external sources.

This increase in demand for external material, coupled with the observed improvement in study performance and the perceived time efficiency during the COVID period, suggests that these external resources were more beneficial to students than the lecture materials provided by professors.


## Descriptive Inference Summary

### Preparation Time
To show the differences of preparation time between before, during and after COVID, blocks of <=5, <=10, etc. hours are created.
To emphasize on the changes a table showing the difference per person is also created.
```{r}
# Inferential summary for preparation times
# | <=10  | <=20h | <=30h | <=40h |
# before c
# during c
intervals = c(0,10, 20, 30, 40, 50, 60, 70, 80, Inf)

cnt_bef <- data_p %>%
       select(test.prep.bef) %>%
        group_by(interval_bef = cut(test.prep.bef, breaks = intervals, right=FALSE)) %>%
        count() %>%
        spread(interval_bef, n)

cnt_dur <- data_p %>%
        select(test.prep.dur) %>%
        group_by(interval_dur = cut(test.prep.dur, breaks = intervals, right=FALSE)) %>%
        count() %>%
        spread(interval_dur, n)

cnt_af <- data_p %>%
        select(test.prep.af) %>%
        group_by(interval_af = cut(test.prep.af, breaks = intervals, right=FALSE)) %>%
        count() %>%
        spread(interval_af, n)



appended <- bind_rows(cnt_bef, cnt_dur, cnt_af) %>%
        mutate(index = c("Before COVID", "During COVID", "After COVID"))

rownames(appended) <- c("Before COVID", "During COVID", "After COVID")
print(appended)
```
The amount of people who prepared for the exam for >= 30 hours decreased during covid considerably from 12 to 6 and stayed down after covid at 6.
This could be caused by making videos available during covid, which stayed available also after covid. If the difference is significant will be shown by a hypothesis test.

```{r}
intervals_diff = c(-Inf, -20, -10, -5, 0, 1, 5, 10, 20, Inf)

# Difference in preparation time
prep_diff <- data_p %>%
        select(test.prep.bef, test.prep.dur, test.prep.af) %>%
        mutate(diff_dur = test.prep.dur - test.prep.bef,
               diff_af = test.prep.af - test.prep.bef) %>%
        select(diff_dur, diff_af)
# prep_diff

cnt_diff_dur <- prep_diff %>%
        select(diff_dur) %>%
        group_by(interval_dur = cut(diff_dur, breaks = intervals_diff, right=FALSE)) %>%
        count() %>%
        spread(interval_dur, n)

cnt_diff_af <- prep_diff %>%
        select(diff_af) %>%
        group_by(interval_af = cut(diff_af, breaks = intervals_diff, right=FALSE)) %>%
        count() %>%
        spread(interval_af, n)


appended_diff <- bind_rows(cnt_diff_dur, cnt_diff_af) %>%
        mutate(index = c("Difference During COVID", "Difference After COVID"))

appended_diff
```

```{r}
# Inferential summary for performance

intervals = c(0, 1, 2, 3, 4, 5, 6, 7, 8, 9, Inf)
intervals_diff = c(-Inf, -5, -3, -2, -1, 0, 1, 2, 3, 5, Inf)
summary_performance <- data_p %>%
        select(performance_bef, performance_dur, performance_af) %>%
        mutate(perf_diff_dur = performance_dur - performance_bef,
               perf_diff_af = performance_af - performance_bef)


perf_cnt_bef <- summary_performance %>%
        select(performance_bef) %>%
        group_by(interval_bef = cut(performance_bef, breaks = intervals, right=FALSE)) %>%
        count() %>%
        spread(interval_bef, n)

perf_cnt_dur <- summary_performance %>%
        select(performance_dur) %>%
        group_by(interval_dur = cut(performance_dur, breaks = intervals, right=FALSE)) %>%
        count() %>%
        spread(interval_dur, n)

perf_cnt_af <- summary_performance %>%
        select(performance_af) %>%
        group_by(interval_af = cut(performance_af, breaks = intervals, right=FALSE)) %>%
        count() %>%
        spread(interval_af, n)

perf_cnt_diff_dur <- summary_performance %>%
        select(perf_diff_dur) %>%
        group_by(interval_dur = cut(perf_diff_dur, breaks = intervals_diff, right=FALSE)) %>%
        count() %>%
        spread(interval_dur, n)

perf_cnt_diff_af <- summary_performance %>%
        select(perf_diff_af) %>%
        group_by(interval_af = cut(perf_diff_af, breaks = intervals_diff, right=FALSE)) %>%
        count() %>%
        spread(interval_af, n)


inferential_summary_perf <- bind_rows(perf_cnt_bef, perf_cnt_dur, perf_cnt_af) %>%
        mutate(index = c("Before COVID", "During COVID", "After COVID"))

inferential_summary_perf_diff <- bind_rows(perf_cnt_diff_dur, perf_cnt_diff_af) %>%
        mutate(index = c("Difference During COVID", "Difference After COVID"))

inferential_summary_perf
inferential_summary_perf_diff
```

```{r}
# Inferential summary for learning sources
summary_learningsources <- data_p %>%
        select(source.bef, source.dur, source.af)

source_cnt_bef <- summary_learningsources %>%
        select(source.bef) %>%
        group_by(source.bef) %>%
        count() %>%
        spread(source.bef, n)

source_cnt_dur <- summary_learningsources %>%
        select(source.dur) %>%
        group_by(source.dur) %>%
        count() %>%
        spread(source.dur, n)

source_cnt_af <- summary_learningsources %>%
        select(source.af) %>%
        group_by(source.af) %>%
        count() %>%
        spread(source.af, n)

inferential_summary_sources <- bind_rows(source_cnt_bef, source_cnt_dur, source_cnt_af) %>%
        mutate(index = c("Before COVID", "During COVID", "After COVID")) %>%
        select(index, External, Internal)

sources_diff_dur <- summary_learningsources %>%
        group_by(source.bef, source.dur) %>%
        count() %>%
        mutate(from = source.bef,
               to = source.dur,
                during = n) %>%
        ungroup() %>%
        select(from, to, during)

sources_diff_af <- summary_learningsources %>%
        group_by(source.bef, source.af) %>%
        count() %>%
        mutate(from = source.bef,
               to = source.af,
               after = n) %>%
        ungroup() %>%
        select(from, to, after)

sources_diff_combined <- bind_cols(sources_diff_dur %>% select(during), sources_diff_af) %>%
        select(from, to, during, after)

inferential_summary_sources
sources_diff_combined


```

```{r}
```